A pipeline to analyse time-course gene expression data

### 2019-07-19 scripts/manuscript.Rmd
added questions about installation in manuscript

EAP:
- Do we need installation instructions for moanin, since its not on CRAN/bioconductor? Also, how its set up now (doing make file, which compiles the documentation, etc), does that prohibit use of, e.g. `install_github` from `devtools`? I.e. not something we can demonstrate in the markdown file.

>>>>

EAP:

- Do we need installation instructions for moanin in this document, since its not on CRAN/bioconductor? Also, how its set up now (doing make file, which compiles the documentation, etc), probably prohibits use of, e.g. `install_github` from `devtools`. If able to call `install_github("NelleV/2019timecourse-rnaseq-pipeline", subdir="bin/moanin", dependencies=TRUE)` would be simpler (would also install the dependencies and get around problems in script)
- I got an error in installation of packages:

```
epurdom-0:2019timecourse-rnaseq-pipeline epurdom$ Rscript scripts/install.R
Loading required package: devtools
Loading required package: usethis
Loading required package: ggfortify
Loading required package: ggplot2
Loading required package: kableExtra
Error in contrib.url(repos, "source") : 
  trying to use CRAN without setting a mirror
Calls: install.packages -> contrib.url
In addition: Warning message:
In library(package, lib.loc = lib.loc, character.only = TRUE, logical.return = TRUE,  :
  there is no package called ‘kableExtra’
Execution halted
```

- `biocLite` is no longer the recommended way to install bioconductor. Instead `BiocManager::install(c('edge', 'NMI'))`. But this is dependent on bioconductor/R version.
